Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2024-11-19 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{xcolor}
\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\T}[1]{\textcolor{orange}{#1}}
%\newcommand{\U}[1]{\textbf{\textit{\textcolor{blue}{#1}}}}
\newcommand{\U}[1]{\textcolor{black}{#1}}
\usepackage{subfigure}
\begin{document}

@@

\begin{appendix}

\section{Code and Data Availability}
\label{sec:appendix_code_and_data}
The source code for ...  is made available under an open source license and is publicly hosted on GitHub.\\
To facilitate a wider community's usage and contributions, we have ensured that the repository is well-documented. The repository includes comprehensive documentation hosted on \emph{ReadTheDocs} that provides an overview of the project, installation instructions, and a guide on how to use the software.

The ... repository, which contains code, additional documentation, and interactive dashboards, is available on GitHub.\footnote{URL: \url{https://github.com/bGuenes/sbi_chemical_abundances}}

\textcolor{red}{To be finalized, do we want to upload data???}
The cleaned data set with outliers removed is publicly available on Zenodo.\footnote{URL: \url{https://zenodo.org/record/8375344}}

   \end{appendix}
\end{document}

>>>>

\usepackage{xcolor}

\newcommand{\todo}[1]{\textcolor{red}{#1}}
\newcommand{\T}[1]{\textcolor{orange}{#1}}
%\newcommand{\U}[1]{\textbf{\textit{\textcolor{blue}{#1}}}}
\newcommand{\U}[1]{\textcolor{black}{#1}}
\usepackage{subfigure}

\begin{document}

@@

% \begin{appendix}

% \section{Code and Data Availability}
% \label{sec:appendix_code_and_data}
% The source code for ...  is made available under an open source license and is publicly hosted on GitHub.\\
% To facilitate a wider community's usage and contributions, we have ensured that the repository is well-documented. The repository includes comprehensive documentation hosted on \emph{ReadTheDocs} that provides an overview of the project, installation instructions, and a guide on how to use the software.

% The ... repository, which contains code, additional documentation, and interactive dashboards, is available on GitHub.%\footnote{URL: \url{https://github.com/bGuenes/sbi_chemical_abundances}}

% \textcolor{red}{To be finalized, do we want to upload data???}
% The cleaned data set with outliers removed is publicly available on Zenodo.%\footnote{URL: \url{https://zenodo.org/record/8375344}}

%   \end{appendix}

\end{document}
